Amazonian Narratives in Presidential Discourse (1985 to 2020)

### 2021-11-06 08112021_Sposito & Silva_Muller_DRAFT.Rmd
#markdown

---
title: "Amazonian Narratives in Presidential Discourse (1985 to 2020)"
author: "Henrique Sposito & Livio Silva-Muller"
date: "11/11/2021"
output: pdf_document
---
# 1 Introduction

@@

# 3 Operationalizing Amazonian narratives: data and methods
# 4 Preliminary Analysis

@@

# Load data
#BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
#amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
#Amazon_speeches <- readRDS("~/GitHub/amazondef/amazon_speeches.Rds")
BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/BR_Presidential_Speeches.Rds") #livio's path
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/amazon_def_year.Rds") #livio's path
Amazon_speeches <- readRDS("~/Documents/GitHub/amazondef/amazon_speeches.Rds") #livio's path

@@

plot(freq_year$year, freq_year$freqn, type = "b",
     main = "Presidential Speeches that mention the Amazon since 1985 in Brazil",
     sub = "Normalized by the number of speeches per year",
     xlab = "Year", ylab = "Frequency")

>>>>

---
title: "Amazonian Narratives in Presidential Discourse (1985 to 2020)"
author: "Henrique Sposito & Livio Silva-Muller"
date: "11/11/2021"
output:
  html_document:
    df_print: paged
---
# 1 Introduction

@@

# 3 Operationalizing Amazonian narratives: data and methods

# 4 Preliminary Analysis

@@

# Load data
#BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
#amazon_def_year <- readRDS("~/GitHub/amazondef/amazon_def_year.Rds")
#Amazon_speeches <- readRDS("~/GitHub/amazondef/amazon_speeches.Rds")
BR_Presidential_Speeches <- readRDS("~/Documents/GitHub/amazondef/BR_Presidential_Speeches.Rds") #livio's path
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/amazon_def_year.Rds") #livio's path
Amazon_speeches <- readRDS("~/Documents/GitHub/amazondef/amazon_speeches.Rds") #livio's path to load data after poldis

@@

plot(freq_year$year, freq_year$freqn, type = "b",
     main = "Presidential Speeches mentioning the Amazon since 1985 in Brazil",
     sub = "Normalized by the number of speeches per year",
     xlab = "", ylab = "Frequency")
